%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods} \label{S:materials_methods}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
We set up an experiment where speech samples were transcribed by a group of listeners. The current section succinctly describes the participating children, the stimuli used, and the experimental setup, while also delve into the causal and statistical framework of analysis.
%
%
%###############################
\subsection{Children} \label{sS:children}
%###############################
%
Thirty two children were selected using a large corpus of \textit{spontaneously spoken speech}, collected by the Computational Linguistics, Psycholinguistics and Sociolinguistics research center (CLiPS). The selection followed a two step procedure \cite{Faes_et_al_2021}. First, a sample of sixteen hearing-impaired children (ten boys, six girls) were selected based on the quality of their registered stimuli. Second, an additional matched sample of sixteen normal hearing children was also selected (six boys, ten girls), and served as a comparison group.
%
\begin{comment}
	Similar designs were used by \citet{Boonen_et_al_2020} and \citet{Faes_et_al_2021}. However, in the former case the number of samples were low, while in the latter, the design was unbalanced and not conducive to appropriate inferences from the pairwise comparisons.
\end{comment}

For the first group, all the hearing-impaired children with cochlear implants (HI/CI) were native speakers of Belgian Dutch, living in Flanders, the Dutch speaking area of Belgium. They were all raised orally using monolingual Dutch, with a limited support of signs. All of the children were screened by the Universal Neonatal Hearing Screening (UNHS), using an automated auditory brainstem response hearing tests for newborns, and all received the cochlear implantation before the age of two. Their medical and audiological records did not ascertain any additional health or developmental issues. Hence, no known additional comorbidities were though present. Finally, at the date of the measurement, they were all enrolled in the mainstream educational system.

For the second group, the sixteen normal hearing children (NH) were closely matched to the HI/CI group based on chronological age. All children were also native speakers of Belgian Dutch, and enrolled in the mainstream educational system. None reported hearing loss or additional disabilities, judged from the UNHS screening procedure and their respective parental report.

The characteristics of the selected children is detailed in Table \ref{tab:characteristics}, at the supplementary section \ref{sSA:characteristics}. 
%
%
%###############################
\subsection{Stimuli} \label{sS:stimuli}
%###############################
%
The stimuli consisted of children's utterances, i.e. sentences of similar length, recovered from previously mentioned CLiPS corpus. More specifically, we use a portion of the corpus that consisted of ten utterances recordings for each of the thirty two selected children, adding to a total of $320$ stimuli. 

The stimuli were documented when the child was telling a story cued by the picture book `Frog, where are you' \citep{Mayer_1969} to a caregiver `who does not know the story'. 

The recordings were orthographically transcribed with the CLAN editor in CHAT format \cite{MacWhinney_2020}. The quality of the stimuli was ensured by selecting utterances with no syntactically ill-formed or incomplete sentences, any background noise, cross-talk, long hesitations, revisions or non-words \citep{Boonen_et_al_2021}. The aforementioned transcriptions were used only in the selection process of the stimuli for the experiment. 
%
\begin{comment}
	under the Design of Experiments (DoE) literature, we would say we have $32$ experimental units with $10$ replicate runs each, making a total of $320$ experimental runs. As it is defined in \citet{Lawson_2015}, an experimental unit is the item under study upon which something is changed, while a replicate run is the experiment conducted with the same factor settings, but using different experimental units. 
\end{comment}
%
%
%###############################
\subsection{Experimental setup} \label{sS:setup}
%###############################
%
The experiment was setup to perform a transcription task in the Qualtrics environment \cite{Qualtrics_2005}. One hundred language students from the University of Antwerp participated. The participants were native speakers of Belgian Dutch, without any particular experience with the speech of hearing-impaired children.

The participants and stimuli were divided into five groups, where each group of $20$ students transcribed $64$ stimuli on their series. The stimuli were presented to the listeners in a random order. As a result, the setup produced $20$ transcriptions per utterance, adding to a total of $6400$ transcriptions. The steps that comprised the task are detailed in the supplementary section \ref{ssSA:transcription}. 
%
\begin{comment}
	present the stimuli based on the \textcolor{blue}{adaptive pairing algorithm} \citep{Pollitt_2012b}?
\end{comment}

The data resulting from the transcription task was then processed and converted into one entropy measure per utterance ($H$), which served as our outcome variable. 

The entropy measure was bounded in the unit interval $[0,1]$, and used as a quantification of (dis)agreement between listeners' transcriptions, where utterances yielding a high degree of agreement between transcribers were considered highly intelligible, and therefore registered a lower entropy $\left( H \rightarrow 0 \right)$. In contrast, utterances yielding a low degree of agreement were considered as exhibiting low intelligibility, and therefore registered a higher entropy $\left( H \rightarrow 1 \right)$ \citep{Boonen_et_al_2021, Faes_et_al_2021}. The procedure followed to calculate the entropies is detailed in the supplementary section \ref{ssSA:entropy}.
%
\begin{comment}
	\textbf{for the experimenter:} Based on \citet{Faes_et_al_2021} we depict the procedure for the experimenter:
	%
	\begin{enumerate}
		\item 1. matching procedure 
		\item selection of suitable stimuli
		\item determine the number of stimuli per judge 
	\end{enumerate}	
\end{comment}
%
%
%###############################
\subsection{Causal framework} \label{sS:causal_frame}
%###############################
%
The analysis was informed by a preliminary work aimed at describing the causal and non-causal factors influencing speech intelligibility. More specifically, the current research uses a Directed Acyclic Graph (DAG) \cite{Pearl_2009, Cinelli_et_al_2021} to describe all the relevant variables though to influence intelligibility. A DAG is a type of \textit{structural causal model} that can be represented, among other ways, by a \textit{causal diagram}. 
%
\begin{figure}[h!]
	%
	\centering
	\begin{tikzpicture}
		% nodes
		\node at (2.55,-0.4) {$H^{O}_{bik}$};
		\node at (4,1) {$U_{b}$};
		\node at (4,-1.3) {$U_{ik}$};
		\node at (1,-0.4) {$H^{T}_{i}$};
		\node at (-0.5,-0.4) {$SI_{i}$};
		\node at (-2,-1.3) {$U_{i}$};
		\node at (-0.9,1.75) {$HS_{i}$};
		%\node at (-0.5,2.7) {$U_{HS}$};
		\node at (-2.2,1.5) {$E_{i}$};
		%\node at (-2,2.7) {$U_{E}$};
		\node at (1.5,1.5) {$PTA_{i}$};
		%\node at (1,2.7) {$U_{P}$};
		\node at (-2.1,1) {$A_{i}$};
		%\node at (-2.8,1) {$U_{A}$};
		
		% paths
		\draw[{Circle[open]}-{latex}{Circle}](0.85,0)--(2.7,0); % Hi->Hik
		\draw[{Circle[open]}-{latex}](4,-1)--(2.7,-0.05); % Uk->Hik
		\draw[{Circle[open]}-{latex}](4,0.7)--(2.7,0.05); % Ub->SIi
		\draw[{Circle[open]}-{latex}](-0.5,0)--(0.85,0); % SIi->Hi
		\draw[{Circle[open]}-{latex}](-2,-1)--(-0.5,0); % Ui->SIi
		\draw[{Circle}-{latex}](-0.45,1.55)--(-0.45,0.05); % HSi->SIi
		\draw[-{latex}](-0.45,1.50)--(-1.90,0.75); % HSi->Ai
		\draw[-{latex}](-0.45,1.5)--(0.85,1.5); % HSi->PTAi
		\draw[{Circle}-{latex}](-2,1.5)--(-0.5,1.5); % Ei->HSi
		\draw[-{latex}](-1.9,1.45)--(-0.47,0.05); % Ei->SIi
		\draw[{Circle}-{latex}](0.95,1.55)--(-0.4,0.05); % PTAi->SIi
		\draw[{Circle}-{latex}](-2,0.75)--(-0.5,0); % Ai->SIi
		%\draw[{Circle[open]}-{latex}](-1.95,2.5)--(-1.95,1.6); % UE->Ei
		%\draw[{Circle[open]}-{latex}](-0.45,2.5)--(-0.45,1.6); % UHS->HSi
		%\draw[{Circle[open]}-{latex}](0.95,2.5)--(0.95,1.6); % UP->PTAi
		%\draw[{Circle[open]}-{latex}](-2.8,0.70)--(-2,0.70); % UA->Ai
		
		% extras
		\node at (0.2,-0.25) {$(-)$}; % symbol
		%
		%\draw[dashed] (-2.55,2.1) rectangle (3.2,-2);
		%\node at (-1.5,-1.8) {\small $i=1,\dots,I$};
		%\draw[dotted, thick] (2.1,0.35) rectangle (5.5,-2);
		%\node at (4.5,-1.8) {\small $k=1,\dots,K$};
		%\draw[dash dot, thick] (2.1,-0.7) rectangle (5.5,2.1);
		%\node at (4.5,1.8) {\small $b=1,\dots,B$};
	\end{tikzpicture}
	%
	\caption[DAG: causal diagram]{DAG: causal diagram describing the relationships among the analyzed variables. Open circles describe latent/unobserved variables, full circles describe observed variables.}
	\label{fig:DAG}
\end{figure}

Figure \ref{fig:DAG} shows the \textit{causal diagram} for our research hypothesis. In the figure, $H^{O}_{bik}$ denote the \textit{observed} entropy replicates nested within children and experimental blocks, where $k=1,\dots,10$ utterances, $i=1,\dots,32$ children, and $b=1,\dots,5$ blocks. Moreover, $H^{T}_{i}$ and $SI_{i}$ denotes the child's \textit{true} entropy and speech intelligibility scores, respectively. In addition, $HS_{i}$ denotes the children's hearing status group, $A_{i}$ their \textit{hearing age}, $PTA_{i}$ their post-implant pure tone average, and $E_{i}$ the etiology of the disease that led to the hearing impairment.

Three main features can be emphasized from the figure. First, the children's \textit{speech intelligibility} and \textit{true} entropy scores are thought to be latent/unobservable variables \cite{Everitt_1984} (drawn with open circles, see supplementary section \ref{sSA:SI} about the appropriate interpretations of the scores). The figure also shows the scores are thought to be inferable from the \textit{observed} entropy replicates. More specifically, we are asserting the \textit{observed} entropy replicates $H^{O}_{bik}$ represent multiple realizations of a child's \textit{true} entropy $H^{T}_{i}$. Finally, we assume the \textit{intelligibility} score $SI_{i}$ is inversely/negatively related to the \textit{true} entropy $H^{T}_{i}$, i.e. the lower the intelligibility the higher the entropy and vice versa, as expected from our the theory. 

Second, the figure reflects the expected multilevel structure of variability in our data. This is particularly important as, by failing to account for the appropriate dependencies in the data, we could be `manufacturing' false confidence in the parameter's estimates, leading us to incorrect inferences \cite{McElreath_2020}. 

Based on the experimental setup described in section \ref{sS:setup}, we anticipated the ten utterances, originated from each of the thirty two children, were also observed within a group of transcribers (series) assigned to the observation, i.e. our data has a hierarchy with children, replicates and block levels ($U_{i}$, $U_{ik}$ and $U_{b}$, respectively). In this regard, we expect that if the experiment was `set up right', the block random effects would explain a small amount of variability in the data, and its inclusion/exclusion in the model would not change the parameter estimates. Moreover, we expect a larger variability between children's \textit{speech intelligibility}, at least larger than the block random effects. Several evidence suggest this is particularly true among HI/CI children \cite{Young_et_al_2002, Peng_et_al_2004, Montag_et_al_2014, Castellanos_et_al_2014, Yanbay_et_al_2014, Nittrouer_et_al_2014, Freeman_et_al_2017}. Finally, we did not had any comparable expectation for the variability in the replicates, as this feature has not been investigated before.

Third, the figure shows the assumed relationship among the relevant variables \cite{Niparko_et_al_2010, Boons_et_al_2012, Gillis_2018, Fagan_et_al_2020}, and how these influence the children's intelligibility of speech. Furthermore, it also reveals we assume the variables are independent, beyond the described relationships. Here follows a description of our causal hypothesis related to the relevant variables.

For \textbf{\textit{hearing status}} ($HS_{i}$), it is clear that its inclusion directly corresponds with the main purpose of the current research endeavor. i.e. compare the levels of \textit{speech intelligibility} among NH and HI/CI children. Yet, we do not have a clear expectation about the levels among the groups. In terms of intelligibility, previous literature suggest that some HI/CI children manage to `catch up' with their NH counterparts \cite{Wie_2010, Habib_et_al_2010, Boons_et_al_2013, Geers_et_al_2013, Bruijnzeel_et_al_2016, Dettman_et_al_2016, Wie_et_al_2020}. However, other studies also indicate HI/CI children never reach similar levels than their NH analogues \cite{Nicholas_et_al_2007, Castellanos_et_al_2014, Chin_et_al_2014, Geers_et_al_2016, Freeman_et_al_2017, Duchesne_et_al_2019, Grandon_et_al_2020}. 

About \textbf{\textit{hearing age}} ($A_{i}$), we expect it to be one of the main responsible for the increase in children's \textit{speech intelligibility}, no mater the children's hearing status \cite{Boonen_et_al_2021}. \textit{Hearing age} is a composite variable constructed by combining the \textit{chronological age} for the NH group, and the \textit{device length of use} for the HI/CI group \citep{Faes_et_al_2021} (see table \ref{tab:characteristics}). The variable tries to approximate the amount of time a child has been actively hearing and developing his(her) language. 

Several studies provide evidence that intelligibility increases with age \cite{Chin_et_al_2001, Chin_et_al_2003, Flipsen_2006, Flipsen_2008, Baudonck_et_al_2009, Bowen_2011, Hustad_et_al_2020}, and no short of evidence has been presented in favor of using others surrogate measures, like \textit{chronological age} \cite{Flipsen_et_al_2006, Habib_et_al_2010, Grandon_et_al_2020} or \textit{age at implantation} \cite{Niparko_et_al_2010, Boons_et_al_2012, Bruijnzeel_et_al_2016, Dettman_et_al_2016}. We argue that the feasibility of using any other proxy measure, largely depends on the assumed reliability of the surrogate to approximate the variable of interest. In that sense, although we recognize \textit{hearing age} is not a `perfect' proxy \cite{Faes_et_al_2021}, we argue it is the most appropriate to test our hypothesis, based on the relevant literature review and its assumed reliability to capture children's language development (although the latter has not been tested). Furthermore, we believe the variable serve two additional purposes: (i) control for sampling bias (expanded in supplementary section \ref{sSA:sampling_bias}), and (ii) de-confound the parameter estimates of \textit{hearing status} \cite{Cinelli_et_al_2021}.

Finally, it is important to highlight that for modeling purposes, using more than one of the aforementioned proxies in tandem is not recommended. It is apparent from the previous description, the three surrogate measures share high similarities in their data construction. This in turn, could cause problems in the modeling procedure, as including variables that provide `similar information' might lead to a statistical problem known as multicollinearity, in which our estimates get biased and less precise \cite{Farrar_et_al_1967}, leading us to incorrect inferences and conclusions.
%
\begin{comment}
	for the NH group uses the child's \textit{age} (at recording), the method cannot use the same variable for the other two groups. This is due to the fact that \textit{age} is merely used as a proxy, for the amount of time a child has been developing his(her) language. In that sense, more appropriate variables to use under the HI/CI group would be e.g. the \textit{device length of use}, which approximates the ``hearing age'' of such children, or their \textit{vocabulary size}, which resembles their "lexical age" \citep{Faes_et_al_2021}. For this research, we consider the \textit{device length of use} as the simplest one to implement.
\end{comment}

For \textbf{\textit{pure tone average}} ($PTA_{i}$), we expect it to have a small or null effect on \textit{speech intelligibility}, as the empirical evidence seem to suggest \cite{Boonen_et_al_2021}. \textit{Pure tone average} is the child's subjective hearing sensitivity, aided or unaided, by their hearing apparatus. 

However, beyond the empirical evidence, the variable was included for two additional reasons. First, given that previous modeling efforts did not capture the full data hierarchy, it is possible that the effects of PTA on \textit{speech intelligibility} has been largely overlooked. Although evidence seem to suggest the variable has no effect, it is also sensible to think that HI/CI children with severe hearing loss, as accounted by the variable, might develop their language at a slower rate. This is especially true, if we consider the signal provided by the cochlear implant is still degraded compared to normal hearing scenarios \cite{Drennan_et_al_2008}. Lastly, a second reason is that the variable might be useful to de-confound the parameter estimates of \textit{hearing status} \cite{Cinelli_et_al_2021}, a purpose shared with the variable \textit{hearing age}. 

In the case of the \textbf{\textit{Etiology}} of the disease that led to the hearing impairment ($E_{i}$), we expect it to have a differential effect on \textit{speech intelligibility}, within the HI/CI group. However, since the severity of the etiology cannot be easily ascertain nor ordered, we cannot foresee the direction of such effects, i.e. genetic factors not necessarily lead to worse levels of language development and intelligibility, than factors related to infections.

The previous assumption does not have a correspondence with the empirical evidence, were the variable was deemed unimportant \cite{Boonen_et_al_2021}. However, we argue that it is possible its effects have also been largely overlooked, due to the lack of statistical control of the full data hierarchy, similar to the PTA case. Moreover, as with its predecessors, the variable might also be useful to de-confound the parameter estimates of \textit{hearing status} \cite{Cinelli_et_al_2021}, assuming our DAG is appropriate.

Finally, it is important to highlight the reason for the absence of other variables, deemed relevant by the literature, in our causal hypothesis.

For the \textbf{\textit{type of cochlear implantation}}, i.e. bilateral or contralateral, the variable was not included because we did not expect it to be related to other variables in the DAG, i.e. the decision on receiving one or the other is solely based on the intelligibility outcome, no matter how the latter is measured. This in turn means that its inclusion/exclusion would not confound our estimates. Additionally, given that most of the children underwent through sequential bilateral implantation (eleven in total), we anticipated the effect of variable already permeates the sample.

For the case of \textbf{\textit{additional disabilities}}, e.g. mental retardation or speech motor problems, as children did not reported any additional comorbidities, the variable was not necessary.

In the case of \textbf{\textit{environmental factors}}, such as communication modality, as the current sample of HI/CI children were raised orally using monolingual Dutch with a limited support of signs, a scenario similar to the NH group (see section \ref{sS:children}), the variable was also not necessary.

Last but not least, \textbf{\textit{gender}} was not included in our hypothesis, as no theoretical nor empirical evidence have been found on its effects \cite{Boonen_et_al_2021}.

As expected, it is possible that other unobserved confounding variables are not accounted by our assumptions, and therefore, our causal diagram. This is true for any type of social, behavioral and educational research. However, we argue that the additional transparency of our approach, and its ability to derive statistical procedures from causal assumptions, is its main strength \cite{McElreath_2020, Yarkoni_2020, Rohrer_et_al_2021}.
%
%
%###############################
\subsection{Statistical analysis} \label{sS:stat_analysis}
%###############################
%
Using the DAG, described in the previous section, we describe the algebraic formalism for our multiple Bayesian probabilistic models \cite{Jaynes_2003}. Each model targeted a different manner in which our research hypothesis could be investigated.

In general terms, every model was composed of two parts: a latent measurement model \cite{Everitt_1984} and a structural equation model \cite{Hoyle_et_al_2014}. For the former, we represented the child's \textit{speech intelligibility} as a latent variable, inversely related to the child's (latent) \textit{true} entropy. Moreover, we modeled the latter as a variable that can be inferred from the (observed) entropy replicates in the following way:
%
\begin{align}
	%
	H^{O}_{bik} & \sim \text{BetaProp} \left( \bar{H}_{bi}, M_{i} \right) \\ 
	%
	\bar{H}_{bi} &= \text{logit}^{-1}( a_{b} -SI_{i} ) \\
	%
	H^{T}_{i} &= \text{logit}^{-1}( -SI_{i} )
	%
\end{align} 

\noindent where $\text{BetaProp}(\mu, \theta)$ defines the beta-proportion distribution with parameters $\mu$ and $\theta$ \cite{Figueroa-Zuniga_et_al_2013, Kruschke_2015}; with $\mu \in [0,1]$ and $\theta>0$. Furthermore, $\bar{H}_{bi}$ represented the ``average'' entropy measure nested within blocks and children ($b=1,\dots,5$ and $i=1,\dots,32$, respectively), while $M_{i}$ denotes the `sample size' of the distribution, possibly nested within children. Furthermore, $H^{O}_{bik}$, $H^{T}_{i}$ and $SI_{i}$ denotes the children's entropy replicates, \textit{true} entropy and \textit{speech intelligibility} score, respectively. Finally, $a_{b}$ represented the block random effects, and $\text{logit}^{-1}(x) = \exp(x) / ( 1 + \exp(x) )$ represented the inverse-logit transformation. 

From the previous algebraic structure we can notice. First, we modeled the average entropy of the replicates with $\mu = \bar{H}_{bi}$, which is a non-linear transformation of the block random effects and the children's \textit{speech intelligibility}. Second, the children's \textit{true} entropy $H^{T}_{i}$ is inversely and non-linearly related to the \textit{speech intelligibility} $SI_{i}$. Third and last, we captured the variability of the entropy replicates using $\theta = M_{i}$. See supplementary section \ref{ssSA:model_variability} for a detailed overview of the implications of using this approach.

For the second component we used a structural model \cite{Hoyle_et_al_2014}. In this portion, different iterations of our research hypothesis were proposed. Hereby we present the general representation from which the others can be derived:
%
\begin{align}
	%
	SI_{i} & = a_{i} + \alpha + \alpha_{E[i], HS[i]} + \beta_{A, HS[i]} (A_{i} - \bar{A}) + \beta_{P, HS[i]} sPTA_{i} 
	%
\end{align}

\noindent where $E_{i}$ and $HS_{i}$ are defined as in the previous section, $A_{i}$ is the \textit{hearing age} in years, while $sPTA_{i}$ is the standardized version of the post-implant pure tone average $PTA_{i}$. Moreover, $a_{i}$ denoted the children's random intercepts, and $\alpha$ the fixed intercept. On the other hand,  $\alpha_{E[i],HS[i]}$ denoted the fixed effects intercept per etiology and hearing status group, while $\beta_{A, HS[i]}$ denoted the slope of \textit{hearing age} per hearing status group. Finally, $\beta_{P, HS[i]}$ described the slope for the standardized pure tone average per hearing status group. 

In the previous algebraic structure it is important to highlight, all parameters are estimated in the logit scale and centered at $sPTA_{i}=0$ and $\bar{A}=5$, the latter denoting the minimum \textit{hearing age} in the sample. This is done to facilitate the interpretation of the parameters.

Thirteen statistical models were derived from the previous general description. Each model expressed one specific way in which our research hypothesis could be investigated. The models were characterized by two aspects: (i) the use of interactions and the selection of interacting variables, and (ii) the `sample size' set to capture the replicates' variability. For the former, the options were: intercept only (model 1), and multivariate regression with no interactions (models 2 to 4), with age and hearing status interaction only (models 5, 8, and 11), with etiology and hearing status interaction only (models 6, 9, and 12), and a full interaction model comprising the previous two (models 7, 10 and 13). In a similar fashion, for the latter the options were: one fixed `sample size' (models 1, 2, 5, 6, and 7), one estimated `sample size' (models 3, 8, 9, and 10), and finally, one `sample size' per child (models 4, 11, 12, and 13), which we dubbed \textit{robust} models. See supplementary section \ref{ssSA:preprocessing}, where we expand about the need for \textit{robust} models. 

Table \ref{tab:models} provides an overview of the parameterization for the full set of proposed models. Notice all used block and children's random effects ($a_{b}$ and $a_{i}$, respectively), as well as the fixed effect intercept ($\alpha$). Moreover, the models with one fixed `sample size' used a value of ten, corresponding to number of utterances per child (see supplementary section \ref{ssSA:model_variability} on its implications for modeling). Finally, all models contemplated the interaction of the standardized pure tone average and the hearing status. The latter was imposed, because the collection of data did not contemplated the measurement of the pure tone average for the NH group. Therefore, the only interpretable parameter is the one estimated for the HI/CI children.

It is important to highlight that for all model implementations, the visual inspection of trace, trace-rank and autocorrelation plots was performed. Additionally, we also evaluated the Gelman-Rubin diagnostic and effective number of samples \cite{Gelman_et_al_2014}. In all cases, the plots and statistics indicated the parameters achieved convergence, good mixing and lack of serial autocorrelation, all necessary requirements to be able to interpret the model estimates.

Additional details concerning the Bayesian implementation of the models, such as the representation of variability in a beta-proportion distribution, the parameters' priors and hyper-priors, the estimation procedure, the data pre-processing phase, and simulation studies are expanded in the supplementary section \ref{sSA:model_details}. 
%
\begin{table}[h!]
	\centering
	\begin{tabular}{|c|lccccccc|} 
		\hline
		& & \multicolumn{7}{c |}{Parameters} \\[0.5ex] 
		\cline{3-9}
		Model & \multicolumn{1}{c}{Name} & $M_{i}$ & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{E[i], HS[i]}$ & $\beta_{A, HS[i]}$ & \beta_{P, HS[i]} \\[0.5ex] 
		\hline\hline
		\rowcolor{gray}
		1 & Intercept only (fixed `size') & 10 & $a_{b}$ & $a_{i}$ & $\alpha$ & -- & -- & -- \\
		2 & No interaction (fixed `size') & 10 & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{HS[i]}$ & $\beta_{A}$ & $\beta_{P, HS[i]}$ \\
		\rowcolor{gray}
		3 & No interaction (one `size')  & $M$ & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{HS[i]}$ & $\beta_{A}$ & $\beta_{P, HS[i]}$ \\
		4 & No interaction (robust) & $M_{i}$ & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{HS[i]}$ & $\beta_{A}$ & $\beta_{P, HS[i]}$ \\ 
		\rowcolor{gray}
		5 & Age interaction (fixed `size') & 10 & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{HS[i]}$ & $\beta_{A, HS[i]}$ & $\beta_{P, HS[i]}$ \\ 
		6 & Etiology interaction (fixed `size') & 10 & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{E[i],HS[i]}$ & $\beta_{A}$ & $\beta_{P, HS[i]}$ \\
		\rowcolor{gray}
		7 & Full interaction (fixed `size') & 10 & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{E[i],HS[i]}$ & $\beta_{A, HS[i]}$ & $\beta_{P, HS[i]}$ \\
		8 & Age interaction (one `size') & $M$ & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{HS[i]}$ & $\beta_{A, HS[i]}$ & $\beta_{P, HS[i]}$ \\
		\rowcolor{gray}
		9 & Etiology interaction (one `size') & $M$ & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{E[i],HS[i]}$ & $\beta_{A}$ & $\beta_{P, HS[i]}$ \\
		10 & Full interaction (one `size') & $M$ & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{E[i],HS[i]}$ & $\beta_{A, HS[i]}$ & $\beta_{P, HS[i]}$ \\
		\rowcolor{gray}
		11 & Age interaction (robust) & $M_{i}$ & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{HS[i]}$ & $\beta_{A, HS[i]}$ & $\beta_{P, HS[i]}$ \\
		12 & Etiology interaction (robust) & $M_{i}$ & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{E[i],HS[i]}$ & $\beta_{A}$ & $\beta_{P, HS[i]}$ \\
		\rowcolor{gray}
		13 & Full interaction (robust) & $M_{i}$ & $a_{b}$ & $a_{i}$ & $\alpha$ & $\alpha_{E[i],HS[i]}$ & $\beta_{A, HS[i]}$ & $\beta_{P, HS[i]}$ \\
		\hline
	\end{tabular}
	\caption[Proposed statistical models]{Proposed statistical models. Parameterizations.}
	\label{tab:models}
\end{table}
%
%
